Yongsang Park

## 1. Skin wounds
```{r}
SRS = c(29, 27, 34, 40, 22, 28, 14, 35, 26, 35, 12, 30, 23, 18, 11, 22, 23, 33)
n = 18
```

## 1a.
If you create a qq plot,
```{r}
qqnorm(SRS)
```

It is a little bit concave down but allowable. So I will say the population distribution is normal.

## 1b.
The test mean is
```{r}
meanSRS = mean(SRS)
meanSRS
```
and test SD is
```{r}
sdSRS = sd(SRS)
sdSRS
```
and alpha = 0.9. We want to know CI for the mean with alpha = 0.9
```{r}
interval = -qt(0.05, n - 1) * sdSRS / sqrt(n)
interval
left = meanSRS - interval
left
right = meanSRS + interval
right
```
so the interval is 22.25346 < mu < 29.07988

## 1c.
H0: mu = 25, HA: mu != 25

and our interval includes 25 in significant level of 0.10, so we do not reject H0.

## 1d.
Is this the strong evidence that the population mean rate is significantly greater than 25 at level alpha=0.05?
```{r}
Tstat = (meanSRS - 25) / (sdSRS / sqrt(n))
pVal = 1 - pt(Tstat, n - 1)
pVal
```
and it is beyond 0.05, so this does not abort the null hypothesis that the population mean rate is greater than 25 at level alpha-0.05.

## 1e.
If the standard deviation of population is given, it means the question will be changed from t test to normal distribution problem. So the answer will be 2, 4.

## 2. Test and power
```{r}
n = 10
```
H_0: mu = 12 vs. H_A: mu != 12
```{r}
alpha = 0.1
sampleMean = 14.2
sampleSD = 4.88
```

## 2a.
The test statistic, T is
```{r}
Tstat = (sampleMean - 12) / (sampleSD / sqrt(n))
Tstat
```
and the p value of this is
```{r}
pVal = 1 - pt(q = Tstat, df = n - 1) + pt(q= -Tstat, df = n - 1)
pVal
```
This value is beyond alpha = 0.1, so we do not reject the null hypothesis.

## 2b.
The confidence interval is
```{r}
interval = qt(p = 1 - alpha / 2, df = n - 1) * sampleSD / sqrt(n)
```
from
```{r}
left = sampleMean - interval
left
```
to
```{r}
right = sampleMean + interval
right
```
and it includes 12. So I can tell a 90% confidence interval includes 12.

## 2c.
We assume the true SD is the sampleSD, and the power is P(reject H_0|H_0 is false).
When mu < 11.37116 or mu > 17.02884, the H_0 is false and we need to reject it.
So we need to find the rejection region when x < 11.37116 or x > 17.02884 when mu_A is 15.
```{r}
pnorm(q = left, mean = 15, sd = sampleSD) + 1 - pnorm(q = right, mean = 15, sd = sampleSD)
```
The power is 0.5673522.