Yongsang Park
## 1. Antibiotic
```{r}
A = c( 8.59, 7.80, 4.11, 8.68, 8.08, 7.86, 6.97, 8.21, 1.72, 8.13, 7.48, 6.33, 8.32, 8.65, 3.06, 8.90)
B = c(5.59, 6.96, 5.25, 6.46, 0.09, 7.70, 3.10, 0.94, 7.00, 7.91, 6.39, 7.45, 5.79, 6.66, 5.91, 6.62, 5.07, 7.25)
```

## 1a.
```{r}
qqnorm(A)
```
```{r}
qqnorm(B)
```

No, each qq plot is not seem to be a normal distribution.

## 1b.
```{r}
boottwo = function(x, y, n.boot) {
  difference = mean(x) - mean(y)
  nx = length(x)
  ny = length(y)
  t.hat = numeric(n.boot) # create vector of length n.boot zeros
  for(i in 1:n.boot) {
    x.star = sample(x=x, size=nx, replace=TRUE)
    y.star = sample(x=y, size=ny, replace=TRUE)
    x.bar.star = mean(x.star)
    y.bar.star = mean(y.star)
    s.x.star = sd(x.star)
    s.y.star = sd(y.star)
    t.hat[i] = ((x.bar.star - y.bar.star) - difference) /
        sqrt((s.x.star^2/nx) + (s.y.star^2/ny))
  }
  return(t.hat)
}

t.hats = boottwo(A, B, 5000)

A.bar = mean(A)
B.bar = mean(B)
A.sd = sd(A)
B.sd = sd(B)
A.n = length(A)
B.n = length(B)

t.obs = (A.bar - B.bar - 0) / sqrt(A.sd^2 / A.n + B.sd^2 / B.n)

m.left.abs = sum(t.hats < -abs(t.obs))
m.right.abs = sum(t.hats > abs(t.obs))
p.value.two.sided = (m.left.abs + m.right.abs) / 5000
cat(sep="", "m.left.abs=", m.left.abs, ", m.right.abs=", m.right.abs,
", B=", B, ", p.value.two.sided=", p.value.two.sided, "\n")
```
I got p value of 0.0724 and it is smaller than the alpha of 0.10. So I reject the null hypothesis.

## 1c.
```{r}
wilcox.test(A, B)
```
I got p-value of 0.006315 and it is way smaller than alpha. I reject null hypothesis also.

## 2. Teachers
```{r}
pi.X = 224 / 395
pi.Y = 126 / 266
alpha = 1 - 0.95

CI = qnorm(1 - alpha / 2) * sqrt(pi.X * (1 - pi.X) / 395 + pi.Y * (1 - pi.Y) / 266)
```
The 95% interval is from
```{r}
pi.X - pi.Y - CI
```
to
```{r}
pi.X - pi.Y + CI
```


## 3. Shoes
```{r}
A = c(379, 378, 328, 372, 325, 304, 356, 309, 354, 318, 355, 392)
B = c(372, 376, 328, 368, 283, 252, 369, 321, 379, 303, 328, 411)
```

## 3a.
Yes, each person wears shoes from each company.

## 3b.
```{r}
D = A - B
qqnorm(D)
```

It is reasonable to assume that it follows the normal population.

## 3c.
Since the difference follows the normal population, I will use t test.
```{r}
d.bar = mean(D)
d.sd = sd(D)
d.n = length(D)
t.obs = (d.bar - 0) / d.sd * sqrt(d.n)
2 * (1 - pt(t.obs, df = d.n - 1))
```
The p value is larger than alpha of 0.05, so we do not reject the null hypothesis.
