# Yongsang Park
# 1. Gambler
## 1a.

$x$    |  1   |  2   |  3   |  4   |  5   |  6
-------|------|------|------|------|------|-----
$p(x)$ | 0.12 | 0.12 | 0.12 | 0.12 | 0.12 | 0.4

## 1b.

The even numbers are 2, 4, and 6.
```{r}
0.12 + 0.12 + 0.4
```

## 1c.

The mean of X is
```{r}
mean = 1 * 0.12 + 2 * 0.12 + 3 * 0.12 + 4 * 0.12 + 5 * 0.12 + 6 * 0.4
mean
```
and the variance of X is
```{r}
var = (1 - mean)^2 * 0.12 + (2 - mean)^2 * 0.12 + (3 - mean)^2 * 0.12 + (4 - mean)^2 * 0.12 + (5 - mean)^2 * 0.12 + (6 - mean)^2 * 0.4
var
```

## 1d.

Each game is independent, so E(2X + Y) = 2E(x) + Y and VAR(2X + Y) = 4VAR(X) + VAR(Y).
Also, the probability of dice does not change when you roll the dice, so you can infer that X and Y have the same mean and the same variance.
E(2X + Y) =
```{r}
3 * mean
```
VAR(2X + Y) =
```{r}
5 * var
```
so the standard deviation is
```{r}
sqrt(5 * var)
```


# 2. Colleges

The possibility that the student will be admitted is 1/6. The total sample size is 7, and only 2 colleges admit.
```{r}
dbinom(x = 2, size = 7, prob = 1/6)
```
The possibility is 0.23 (rounded to two decimal)

# 3. Airlines
## 3a
The possibility that the passenger will not show up is 0.05. It means the possibility that the passenger will show up is 0.95.
The mean o binomial random variable is (size * probability)
```{r}
52 * 0.95
```
About 49 people will show up.

## 3b
The possibility that the passenger will show up is 0.95, the total sample size is 52, and the possibility that we want to know is when x = 51.
```{r}
dbinom(x = 51, size = 52, prob = 0.95)
```
The probability that 51 passenger will show up is 0.1900541.

## 3c
The expected number means mean, and it is (size * probability). The variance is (size * probability * (1 - probability)).
The expected number of passengers is
```{r}
52 * 0.95
```
and the expected variance of passengers is
```{r}
52 * 0.95 * 0.05
```

# 4 Goombas and Koopa Troopas
## 4a
The mean and standard variation of Goombas are 12 inches and 6 inches. The probability that a randomly chosen Goomba has a height between 13 and 15 inches is
```{r}
pnorm(q = 15, mean = 12, sd = 6) - pnorm(q = 13, mean = 12, sd = 6)
```

## 4b.
Koopa Troopas have normally distributed heights with mean 15 inches and standard deviation 3 inches.
The probability that a randomly chosen Koopa Troopa is taller than 75% of Goombas is
```{r}
1 - pnorm(q = qnorm(p = 0.75, mean = 12, sd = 6), mean = 15, sd = 3)
```

## 5. Temperatures
The Fahrenheit is following N(90, 5^2).
## 5a.
The probability that one randomly selected instance of the process will have operating temperature greater than 93.8 Fahrenheit is
```{r}
1 - pnorm(q = 93.8, mean = 90, sd = 5)
```

## 5b.
C (Celsius) is equal to 5 * (F - 32) / 9,
so E(5 * (F - 32) / 9) = (5/9)(E(F) - 32) and
VAR(5 * (F - 32) / 9) = (25/81)VAR(F).
```{r}
MeanC = (5/9)*(90 - 32)
MeanC
VarC = (25/81) * 25
VarC
```

## 5c.
The probability that randomly selected thermometer indicates below 29 Celsius is
```{r}
pnorm(q = 29, mean = MeanC, sd = sqrt(VarC))
```

## 5d.
The Celsius temperature x such that the probability that the operating temperature in Celsius of one instance is less than x is .25 is
```{r}
qnorm(p = 0.25, mean = MeanC, sd = sqrt(VarC))
```

