Yongsang Park

## 1. Test for dissolved oxygen
SRS (n = 44)
```{r}
SRS = c(11.53, 8.35, 11.66, 11.54, 9.83, 5.92, 7.14, 8.41, 8.99, 13.81, 10.53, 7.4, 6.7, 8.42, 8.4, 8.18, 9.5, 7.22, 9.87,
6.52, 8.55, 9.75, 9.27, 10.61, 8.89, 10.01, 11.17, 7.62, 6.43, 9.09, 8.53, 7.91, 8.13, 7.7, 10.45, 11.3, 10.98, 8.14,
11.48, 8.44, 12.52, 10.12, 8.09, 7.34)
```
sample mean = 9.14
population sd = 2
H0: mean = 10 vs. Ha: mean != 10
alpha = 0.02

## 1a.
The test statistic is Z = (sampleMean - populationMean) / (SD / sqrt(n))
So the test statistic is
```{r}
test_statistic = (9.14 - 10) / (2 / sqrt(44))
test_statistic
```
and the p-value is P(Z < test_statistic) = P(Z < -2.852297)
```{r}
p_value = pnorm(test_statistic)
p_value
```

## 1b.
The point where the alpha is 0.02 is
```{r}
qnorm(0.02 / 2)
```
and the test statistic is below that point. Also, the p value is small enough to reject the H0.
So I can reject the null hypothesis.

## 2. Pain-killing drug
200 doses

population mean: 2.0

population sd: 0.1

H0: mean = 2.0

Ha: mean != 2.0

If we make a table,

|        |Reject H0               | Not Reject H0     |
|--------|------------------------|-------------------|
|H0 True |type 1 error / alpha    |1 - alpha          |
|H0 False|1 - beta                |type 2 error / beta|


## 2a.
The test mean was 2.0, which means H0 is true, but it reject H0. So it has type 1 error.

the answer is alpha.

## 2b.
The test mean was not 2.0, or H0 is false, and the test assert the mean is different.

The answer is 1 - beta.

## 2c.
The test mean was 2.0, or H0 is true, and it does not reject H0.

The answer is 1 - alpha.

## 2d.
The test mean was not 2.0, or H0 is false, but it does not reject H0, which is type 2 error.

The answer is beta.